A linearization procedure for constrained multibody systems

### 2012-03-25 PetersonGedeHubbard2012.tex
Editted intro.

The goal of the following calculations is to concretely establish the first
order relationships (about an arbitrary equilibrium point) between an arbitrary
choice of independent coordinates and speeds, and the time-derivatives of all
coordinates and speeds (both independent and dependent).  This enables several
common tasks: (1) stability analysis, (2) control system design, (3) control system design with output feedback based
upon quantities that are dependent (i.e., not state variables), (4)
determination of measurement equations for use in Kalman filter design when
measured quantities are at the acceleration level (i.e., accelerometers).  The
formalism presented here is generic enough to cover most examples of
time-varying constrained multibody systems with arbitrary external inputs and
arbitrary specified quantities.  This procedure has been created for systems
whose equations of motion have been found with Kane's Method; this ensures that
only ordinary differential equations are generated and no differential
algebraic equations arise.  While the use of Kane's Method is not required for
this procedure, equations of motion which can be completely described by a series
of ODEs is a requirement.

>>>>

The goal of the following calculations is to concretely establish the first
order relationships (about an arbitrary equilibrium point) between an arbitrary
choice of independent coordinates and speeds, and the time-derivatives of all
coordinates and speeds (both independent and dependent).  This enables several
common tasks: (1) stability analysis, (2) control system design, (3) control
system design with output feedback based upon quantities that are dependent
(i.e., not state variables), (4) determination of measurement equations for use
in Kalman filter design when measured quantities are at the acceleration level
(i.e., accelerometers).  The formalism presented here is generic enough to
cover most examples of time-varying constrained multibody systems with
arbitrary external inputs and arbitrary specified quantities.  This procedure
has been created for systems whose equations of motion have been derived with
Kane's Method; while this is not a strict requirement, systems
which can be completely described by a set of ODEs is (i.e., no DAEs).
